Creating figures for the paper

### 2024-07-30 infercnv/reports/paper_figures.Rmd
add lolliplotting
change ref files from channel to file, split infercnv run script

```{r}
# load the metadata
sm <- readr::read_tsv("/lustre/scratch125/casm/team268im/lh22/Rheumatoid_Arthritis_Paper/Data/MetaData/sample_meta.tsv")

# load the muts and convert to list
load("/lustre/scratch125/casm/team268im/lh22/Rheumatoid_Arthritis_Paper/Figures/Figure_2/LCM_NanoSeq_Overlap/GOI/pileup_muts.rda")
muts <- list(exome = exome_muts,
             LCM = LCM_muts,
             targeted = nano_muts,
             pileup = pileup_muts)

>>>>

```{r}
lh22_dir <- "/lustre/scratch125/casm/team268im/lh22/Rheumatoid_Arthritis_Paper/"

# load the metadata
sm <- readr::read_tsv(file.path(lh22_dir, "Data/MetaData/sample_meta.tsv"))

# load the muts and convert to list
load(file.path(lh22_dir, "Figures/Figure_2/LCM_NanoSeq_Overlap/GOI",
               "pileup_muts.rda"))
muts <- list(exome = exome_muts,
             LCM = LCM_muts,
             targeted = nano_muts,
             pileup = pileup_muts)

# lollipopPlot
